Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-07 paper.tex
fichero de compilacion añadido

\subsubsection{GPUs}
As it has been said before, an instance is based in a VM 
which is running on a real node with its own virtualized 
components, so it is possible that AWS could use a virtualization 
framework to offer GPU services to all the instances.
Therefore, we need to verify if the GPUs showed in the instances are 
non-virtualized GPUs so, we have executed the NVIDIA SDK test called 
{\tt bandwidthtest}. As it is shown in the Table~\ref{table:bwt}, as the bandwidth achieved 
in this test is higher than the network bandwith, it reveals that it is a 
real GPU. 
\begin{table}[htb]
\renewcommand{\arraystretch}{1.3}
\caption{NVIDIA SDK {\tt bandwidthtest} execution transfering 32MB using pageable memory using local GPU.}
\label{table:bwt}
\tabcolsep=0.09cm
\begin{center}\begin{tabular}{cccc}
Name &  Data Movement & Network & BandWidth \\ \hline \hline
g2.2xlarge & Host to Device & Hight& 3,004 MB/s \\ \hline
g2.2xlarge & Device to Host & Hight& 2,809 MB/s\\ \hline
g2.8xlarge & Host to Device & 10 Gb& 2,814 MB/s\\ \hline
g2.8xlarge & Device to Host & 10 Gb& 3,182 MB/s\\ \hline
\end{tabular}\end{center}\end{table}

@@

\begin{table}[htb]
\renewcommand{\arraystretch}{1.3}
\caption{NVIDIA SDK {\tt bandwidthtest} execution transfering 32MB using pageable memory using {rCUDA}.}
\label{table:bwtrcuda}
\tabcolsep=0.09cm
\begin{center}\begin{tabular}{cccc}
Scenario &  Data Movement & Network & BandWidth \\ \hline \hline
A & Host to Device & Hight& 127 MB/s \\ \hline
A & Device to Host & Hight& 126 MB/s\\ \hline
B & Host to Device & 10 Gb& 858 MB/s\\ \hline
B & Device to Host & 10 Gb& 843 MB/s\\ \hline
\end{tabular}\end{center}\end{table}

>>>>

\subsubsection{GPUs}
As it has been said before, an instance is based in a VM 
which is running on a real node with its own virtualized 
components, so it is possible that AWS could use a virtualization 
framework to offer GPU services to all the instances.
Therefore, we need to verify if the GPUs showed in the instances are 
non-virtualized GPUs so, we have executed the NVIDIA SDK test called 
{\tt bandwidthtest}. As it is shown in the Table~\ref{table:bwt}, as the bandwidth achieved 
in this test is higher than the network bandwith, it reveals that it is a 
real GPU. 
\begin{table}[htb]
\renewcommand{\arraystretch}{1.3}
\caption{NVIDIA SDK {\tt bandwidthtest} execution transfering 32MB using pageable memory using local GPU.}
\label{table:bwt}
\tabcolsep=0.09cm
\begin{center}\begin{tabular}{cccc}
Name &  Data Movement & Network & BandWidth \\ \hline \hline
g2.2xlarge & Host to Device & High& 3,004 MB/s \\ \hline
g2.2xlarge & Device to Host & High& 2,809 MB/s\\ \hline
g2.8xlarge & Host to Device & 10 Gb& 2,814 MB/s\\ \hline
g2.8xlarge & Device to Host & 10 Gb& 3,182 MB/s\\ \hline
\end{tabular}\end{center}\end{table}

@@

\begin{table}[htb]
\renewcommand{\arraystretch}{1.3}
\caption{NVIDIA SDK {\tt bandwidthtest} execution transfering 32MB using pageable memory using {rCUDA}.}
\label{table:bwtrcuda}
\tabcolsep=0.09cm
\begin{center}\begin{tabular}{cccc}
Scenario &  Data Movement & Network & BandWidth \\ \hline \hline
A & Host to Device & High& 127 MB/s \\ \hline
A & Device to Host & High& 126 MB/s\\ \hline
B & Host to Device & 10 Gb& 858 MB/s\\ \hline
B & Device to Host & 10 Gb& 843 MB/s\\ \hline
\end{tabular}\end{center}\end{table}
